
## Overview

dstools gives Datasketch a compendium of useful and generic functions in order to improve other packages work.


## Installation

Install the development version of dstools from GitHub with:

``` r
# install.packages("devtools")
remotes::install_github("datasketch/dstools")
```

## Usage

Some of the main functions of this package are:

- Pipe `%||%` evaluates nullity between two objects and:

  a) **return x** if neither x nor y is NULL, empty or NA
  b) **return x** if y is NULL, empty or NA
  c) **return y** if x is NULL, empty or NA
  
```{r}
library(dstools)

# **return x** if neither x nor y is NULL, empty or NA
x <- "pepe"
y <- "x"

x %||% y

# **return x** if y is NULL, empty or NA
x <- "pepe"
y <- NULL

x %||% y

# return y if x is NULL, empty or NA
x <- NULL
y <- "x"

x %||% y
```


- `remove_accents` eliminates accents from vocals and return the given string value without them

```{r}
remove_accents("Thís accénts áré góing to bé removéd")
```

- `is.empty` evaluates object emptiness

```{r}
# Empty object
empty_object <- list()
is.empty(empty_object)

# Not empty object
non_empty_object <- "hello"
is.empty(non_empty_object)
```

- `na_to_chr` replace NA values with a given value

```{r}
sample <- c("text 1", NA, "text 2", "text 3", NA)

na_to_chr(sample, "ex_na")
```


- `na_proportion` estimates the proportion of NA values in a vector

```{r}
sample <- c(NA, NA, 1,2,3,4)
na_proportion(sample)
```

